\Huge \textcolor{titleTextColor}{ \textsf{\textbf{ \fontsize{85}{60}\selectfont GRASS GIS: a peer-reviewed scientific platform and future research repository }} }

### 2015-03-30 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
2015_EGU_G7_PeerReview_SciPlatform poster: bib cleanup; two TODOs added
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64941 15284696-431f-4ddb-bdfa-cd5b030d7da7

% For blibliography styling
\usepackage{natbib}

@@

\begin{minipage}{0.5\linewidth}
\includegraphics[width=\textwidth, trim={0 180 0 0}, clip]{rdiversity}
Landscape diversity according to shannon index in near Charlotte (North Carolina, USA).
\end{minipage}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Conclusions}}{
% TODO: review the points, it should be the highlight or something like that
% TODO: style of bullets is strange
\begin{itemize}
 \item Algorithms and models once included into GRASS GIS are still available.
 \item GRASS GIS development team takes care of API related updates and operating system related changes.
 \item Scientists are using highly specialized tools implemented by other people when having both scientific publication and source code at hand.
 \item New research and tools is build upon the existing one.
\end{itemize}
}

>>>>

% For bibliography styling
%% TODO: all names should be abbreviated
\usepackage{natbib}

@@

\begin{minipage}{0.5\linewidth}
\includegraphics[width=\textwidth, trim={0 180 0 0}, clip]{rdiversity}
Landscape diversity according to Shannon index in near Charlotte (North Carolina, USA).
\end{minipage}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Conclusions}}{
% TODO: review the points, it should be the highlight or something like that
% TODO: style of bullets is strange
\begin{itemize}
 \item Algorithms and models once included into GRASS GIS remain available long term.
 \item GRASS GIS development team takes care of API related updates and operating system related changes.
%% TODO: what does that mean?:
 \item Scientists are using highly specialized tools implemented by other people when having both scientific publication and source code at hand.
 \item New research and tools is build upon the existing one.
\end{itemize}
}
